---
title: "Trusting Collaboration"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(htmlwidgets, quietly=TRUE)
library(ndtv, quietly=TRUE)
library(network, quietly=TRUE)
library(tsna, quietly=TRUE)
library(scatterplot3d)

num_authors <- 25
iter = 15
adj_list <- matrix(0L, nrow=num_authors, ncol=num_authors)
diag(adj_list) <- -1
auth_types <- rbinom(n=num_authors,size=1,prob=0.5)
```

```{r Data, include=FALSE}
library(ndtv)
library(tsna)
library(htmlwidgets)

cols_without_1 <- function(alist){
    num_cols <- dim(alist)[2]
    # List of cols
    to_return <- vector('integer')
    for (cur_col in 1:num_cols){
        col_vec <- alist[,cur_col]
        if (all(col_vec != 1)) {
            to_return <- c(to_return, cur_col)
        }
    }
    return(to_return)
}

net_list = list()

# Time loop
for (t in 1:iter){
    print(paste0("****** Time t=",t))
    # Loop over (shuffled) authors
    shuffled_authors <- sample(1:num_authors)
    for (cur_auth in shuffled_authors){
        print(paste0("*** Resolving 1s for author #", cur_auth))
        # First resolve any 1s
        unresolved <- which(adj_list[cur_auth,] == 1)
        if (length(unresolved) > 0){
            for (unresolved_ind in unresolved){
                # Check the types
                if (auth_types[cur_auth] == auth_types[unresolved_ind]){
                    print(paste0("Author ",cur_auth," and author ",unresolved_ind," SUCCESSFULLY coauthor!"))
                    adj_list[cur_auth, unresolved_ind] <- 3
                    adj_list[unresolved_ind, cur_auth] <- 3
                } else {
                    print(paste0("Author ", cur_auth," and author ", unresolved_ind," FAIL to coauthor"))
                    adj_list[cur_auth, unresolved_ind] <- 2
                    adj_list[unresolved_ind, cur_auth] <- 2
                }
            }
        }
    }
    for (cur_auth in shuffled_authors){
        # Then form new links, IF this author hasn't been chosen yet
        if (any(adj_list[cur_auth,] == 1)) {
            print(paste0("*** Author ",cur_auth," already chosen. No new links."))
        } else {
            print(paste0("*** Forming new links for author ",cur_auth))
            # Candidates must have 0 with cur_auth AND not have a 1 with anyone else!
            havent_talked <- which(adj_list[cur_auth,] == 0)
            not_talking <- cols_without_1(adj_list)
            candidates <- intersect(havent_talked, not_talking)
            print("Candidates:")
            print(candidates)
            # Randomly choose one of the candidates, if any
            if (length(candidates) > 0){
                if (length(candidates) == 1){
                    chosen_cand <- candidates[1]
                } else {
                    chosen_cand <- sample(candidates, 1)
                }
                print(paste0("Author #", cur_auth, " forming link with ",chosen_cand))
                adj_list[cur_auth, chosen_cand] <- 1
                adj_list[chosen_cand, cur_auth] <- 1
            }
        }
    }
    net_list[[t]] = print(adj_list)
}

# NOW do network stuff
library(network)

net_list = lapply(net_list, FUN = function(x) as.network(x, matrix.type="adjacency", directed=FALSE,ignore.eval=FALSE, names.eval="weight"))

test = networkDynamic(network.list = net_list, create.TEAs = TRUE)
```

```{r Movie}
compute.animation(test)

wid = render.d3movie(test,
                     vertex.cex = 1.2,
               edge.lwd = function(slice){
                 lwd = slice%e%"weight"
                 lwd[lwd == 2] = 0
                 return(lwd * 2)
               },
               edge.col = function(slice){
                 col = slice%e%"weight"
                 col[col == 2] = 0
                 return(col)
                 },
               vertex.col = auth_types,
               output.mode = 'htmlWidget')
```


## When is Trust Important?

- Investment/Sunk costs are high
- Relationship failure has consequences
- Limited number of connections can be formed

## Model Details

We used a pseudo Temporal Exponential Random Graph Model (TERGM) to model network formation. We start with a number of isolates ($\alpha$), and a set number of iterations (t). At time = t, we randomly allow each node to initiate a connection with another node. If a node already has a partner, it is not eligible to be paired with. At time = t + 1, each of these connections are tested for affinity (trust). If both nodes are of the same sub-type, the connection is solidified as a trusting relationship. If nodes are of a different sub-type, the connection is dropped.

## We assume

- Individuals meet in dyads, and that those dyads later form groups
- Individuals meet uniformly at random
- Individuals pair based on only one criteria
- Binary trust/no trust

## Modeling Trust Network Formation

Model with `r num_authors` authors, `r iter` iterations.

```{r Model 1, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wid
```

## Practical Case - Coauthorship Networks

- Significant time investment
- Allows for comparison between fields with varying number of sub-fields and co-authorship norms
- Allow for matching sub-types across fields, within which sub-types cannot match

## Future Improvements

- Remove previously mismatched dyads from the list of potential new connections at each time
- Allow for multiple sub-types of nodes
- Allow for multiple sub-types per node
- Allow for node 'satiation,' meaning nodes will stop looking for new partners once a threshold is reached (collusion within clusters).

## Thank you

```{r Prism, echo=FALSE}
timePrism(test, at=c(1, 5, 10), displaylabels = FALSE, planes = TRUE)
```





